---
title: "Module 9 - Goal Programming"
author: "Tom Scarberry"
date: "11/1/2021"
output:
  pdf_document: default
  word_document: default
---


#  Emax Corporation wishes to Maximize Z=P-6C-3D; where P=total profit of new products, C=change of employment, and D=decrease in next year's earnings

# Define terms for the problem

## y1p is positive change of employment level from 50 and y1m is negative change of employment level from 50

## y2p is positive change in next year's earnings and y2m is negative change in next year's earnings

## x1 = production of product 1

## x2 = production of product 2

## x3 = production of product 3

# Algebraic expression of terms for the problem

## 6x1 + 4x2 + 5x3 - (y1p - y1m) = 50

## 8x1 + 7x2 + 5x3 - (y2p - y2m)  = 75

## P = 20x1 + 15x2 + 25x3

# Management's Objective Function

## Maximize 20x1 + 15x2 + 25x3 - 6 y1p - 6 y1m - 3 y2m


# LP Model for Emax Corp

## /* Objective function */

## max:  20x1 + 15x2 + 25x3 - 6 y1p - 6 y1m - 3 y2m;

## // Constraints

## 6x1 + 4x2 + 5x3 + y1m - y1p = 50;

## 8x1 + 7x2 + 5x3 + y2m - y2p = 75;


## Load lp library and load lp file for Emax Corp
```{r echo=TRUE, results='hide', warning=FALSE}
library(lpSolveAPI)
goal <- read.lp("goal_programming_assignment.lp")

```

## Emax linear model
```{r}
goal
```

## Solve Emax Corp linear model
```{r}
solve(goal)
get.objective(goal)
get.variables(goal)

```

# Emax Recommendation

## Emax should produce 15 units of product 3 for an objective function score of 225.  This creates an employment level of 75, which is 25 over the constraint of 50.




