---
title: "Module 4 - Solve LP Model Using R"
author: "Tom Scarberry"
date: "9/26/2021"
output:
  pdf_document: default
  word_document: default
---
## Load libraries
```{r echo=TRUE, results='hide', warning=FALSE}
library(lpSolve)
library(lpSolveAPI)
```


## Objective function with 9 variables, each plant, and size combination
```{r}
lprec <- make.lp(0,9)

```

## Create the Objective function and change to maximization (output hidden for ease of reading knit file)
```{r echo=TRUE, results='hide'}
set.objfn(lprec, c(300,360,420,300,360,420,300,360,420))
lp.control(lprec, sense='max')


```

## Add constraints for plant excess capacity
```{r}
add.constraint(lprec,c(1,1,1,0,0,0,0,0,0),"<=",750)
add.constraint(lprec,c(0,0,0,1,1,1,0,0,0),"<=",900)
add.constraint(lprec,c(0,0,0,0,0,0,1,1,1),"<=",450)
```

## Add constraints for product demand per day
```{r}
add.constraint(lprec,c(1,0,0,1,0,0,1,0,0),"<=",750)
add.constraint(lprec,c(0,1,0,0,1,0,0,1,0),"<=",1200)
add.constraint(lprec,c(0,0,1,0,0,1,0,0,1),"<=",900)

```

## Add constraints for excess holding space for product at each plant
```{r}
add.constraint(lprec,c(12,15,20,0,0,0,0,0,0),"<=",13000)
add.constraint(lprec,c(0,0,0,12,15,20,0,0,0),"<=",12000)
add.constraint(lprec,c(0,0,0,0,0,0,12,15,20),"<=",5000)

```

## Add constraints for equal labor distribution across plants
```{r}
add.constraint(lprec,c(6,6,6,-5,-5,-5,0,0,0),"=",0)
add.constraint(lprec,c(0,0,0,-5,-5,-5,10,10,10),"=",0)

```

## Add variable and constraint names
```{r}
ColNames <- c("Plant1_Small","Plant1_Medium","Plant1_Large","Plant2_Small","Plant2_Medium","Plant2_Large","Plant3_Small","Plant3_Medium","Plant3_Large")
RowNames <- c("Plant1_capacity","Plant2_capacity","Plant3_capacity","Small_demand","Medium_demand","Large_demand","Plant1_space","Plant2_space","Plant3_space","Labor_split1","Labor_split2")
dimnames(lprec) <- list(RowNames,ColNames)

```

## Print out the model
```{r}
lprec

```

## Solve the LP problem
```{r}
solve(lprec)

```

## Objective and variables that deliver the optimal objective value
```{r}
get.objective(lprec)
get.variables(lprec)

```
# Recommendation
# Plant 1 should produce 177.8 medium size and 516.7 large size units per day
# Plant 2 should produce 166.7 small size and 666.7 medium size units per day
# Plant 3 should produce 416.7 small size units per day
# The profit for this production schedule will be $696,000 per day

```{r}

```


