---
title: "Module 6 - The Transportation Model"
author: "Tom Scarberry"
date: "10/12/2021"
output:
  pdf_document: default
  word_document: default
---

# Problem formulation

## /* Objective function */

## min: 622 x11 + 614 x12 + 630 x13 + 641 x21 + 645 x22 + 649 x23;

## /* Constraints */

## x11 + x12 + x13 <= 100;

## x21 + x22 + x23 <= 120;

## x11 + x21 = 80;

## x12 + x22 = 60;

## x13 + x23 = 70;

## Load library
```{r echo=TRUE, results='hide', warning=FALSE}
library(lpSolveAPI)
```


## Load the problem formulation lp file
```{r}
x <- read.lp("transportation_assignment.lp")

```

## Solve the transportation problem
```{r}
solve(x)


```

## Objective and variable values
```{r}
get.objective(x)
get.variables(x)

```

## Add variable and constraint names
```{r}
ColNames <- c("PlantA_WH1","PlantA_WH2","PlantA_WH3","PlantB_WH1","PlantB_WH2","PlantB_WH3")
RowNames <- c("PlantA_capacity","PlantB_capacity","WH1_demand","WH2_demand","WH3_demand")
dimnames(x) <- list(RowNames,ColNames)

```

## Print out the model with column and row names
```{r}
x

```


# Recommendation
# Plant A should produce 100 units and ship 60 to Warehouse 2 and 40 to Warehouse 3
# Plant B should produce 110 units and ship 80 to Warehouse 1 and 30 to Warehouse 3
# This leaves production slack available of 10 units in Plant B 
# The production and transportation costs will be $132,790 per month

